Replication on multicore considering hierarchy and characteristics of the network

### 2013-02-25 paper.tex
Integrated some more concrete ideas on which algorithms to work on.

\paragraph{What do you want to enable?} Increase algorithm performance
on multicores by applying distributed principles, particularly
replication. Consistency using hierarchical group communication.

@@

\paragraph{What's the related work?} People do replication to deal
with scalability challenges on multicores, e.g.\
databases~\cite{Salomie2011, Wiesmann2000} and operating
systems~\cite{fos:osr09, tornado:osdi99, barrelfish:sosp09}. But they
don't to it properly. They do not consider machine characteristics.

\paragraph{What new idea(s) will solve the problems?} Consider machine
characteristics and keep in mind, that multicore machines are
different. \\
{\footnotesize Example: sequential consistency on shared memory, do
  not really need to have primary backup.}

>>>>

\paragraph{What do you want to enable?} Increase algorithm performance
on multicores by applying distributed principles, particularly
replication. The challenge then is to guarantee consistency. Previous
work was using primary copy protocols to do that~\cite{Wiesmann2000}, a
passive replication scheme (i.e.\ nodes do not have to contact all
replicas). They do that because they claim that it is not suitable for
clients to know about replication details.

@@

\paragraph{What's the related work?} People do replication to deal
with scalability challenges on multicores, e.g.\
databases~\cite{Salomie2011, Wiesmann2000} and operating
systems~\cite{fos:osr09, tornado:osdi99, barrelfish:sosp09}. But they
don't to it properly. They do not consider machine characteristics or
apply the wrong distributed technologies.

\paragraph{What new idea(s) will solve the problems?} We do a
hierarchical group communication, which implements an atomic
broadcast on multicore machines. It has message complexity of
$O(\frac{n}{2})$ and time complexity $O(log(n))$ as opposed to
algorithms from traditional distributed systems having $O(2)$ message
complexity and $O(n)$ time complexity. %
\\
{\footnotesize Example: sequential consistency on shared memory, do
  not really need to have primary backup.}
